---
title: "__ Data Processing (change title to reflect your experiment)"
output: html_notebook
---


```{r download data and examine file sizes for cutoff point}
library(aws.s3)
library(tidyverse)

## The purpose of this file is to download the raw data objects from AWS and to put them in a local data folder. Following that, please process the raw data files until ONE SINGLE .csv file is produced. This final .csv should contain one trial per line. 

#Provides a list of all of the buckets in the list 
bucketlist("s3://task-data-raw/")

#define your aws-s3 folder
aws_folder ="bills-task-pilot"

#download all the files from that folder to your raw library 
system(paste("aws s3 cp s3://task-data-raw/",aws_folder," ../data/raw --recursive", sep = ""))

#creat a list of the files and their sizes
raw_files = file.info(list.files ("../data/raw", 
                                  full.names =TRUE, 
                                  recursive=FALSE)) %>% 
  arrange(size) %>% 
  mutate(size_kb = size/1000)

ggplot(raw_files,aes(x=size_kb)) +
  geom_histogram(color = "black") 


```


```{r}
#define your kb file size criteria for files you wish to remove
size_criteria = 150
#shell(paste("find ..\\data\\raw\\ -type f -size -150k -exec mv ..\\data\\raw ..\\data\\raw\\did_not_finish\\+"))
#system(paste("mv ../data/raw ../data/raw/did_not_finish\ " ))

#above code does not work (yet), please manually move the files that are too small according to the histogram into the did_not_finish folder to proceed.


path =  "../data/raw" #path to the raw files (of good size)

#get all csv files and combine them
csv_files <- fs::dir_ls(path, regexp = "\\.csv$") 

#map dataframe on to csvs
d = csv_files %>% 
  map_dfr(read_csv)


# Process the data in the next few chunks. The final output of this data processing should be one long-format csv that contains one trial per line.

```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

