---
title: "[YOUR STUDY] Data Analysis"
output: html_notebook
---

We use groundhog (https://groundhogr.com/) to manage our packages. Groundhog makes sure that our package versions are consistent with the current date. This way, everyone will be using packages from the same date to prevent any issues related to package versioning in future analyses. 

To use groundhog, please: 
(1) make sure that you have the latest version of R/ RStudio installed; 
(2) install RTools
(3) make sure you are in a new R Session


The R Version used to create this file is: `R version 4.3.0 (2023-04-21 ucrt)`. You can change this out with your own version of R if you are using this template to create your own analysis. If you are reproducing another person's analysis, please download the version of R used by the previous person to ensure a proper reproduction of the code.

You can identify your version of R by typing `version` into the R Console

You can switch your R version by pressing `Tools` > `Global Options` > `R Version`


```{r download packages and format csv to prepare for analysis}

# if you need to install groundhog
#if(!suppressWarnings(require(groundhog))){remotes::install_github('CredibilityLab/groundhog')}

#call groundhog
library("groundhog")



# put all packages in and call groundhog
pkgs <- c(
    "Rmisc",
    "tidyverse",
    "lme4",
    "lmerTest",
    "jsonlite",
    "car",
    "simr",
    "knitr"
    )

pkgs_all <- c(pkgs)

# call groundhog. Change out the date for today's date (unless you are running an old analysis)
groundhog.library(pkgs_all, "2023-04-23")

# this line of code runs better in Windows
#groundhog.library(pkgs_all, "2023-04-23",ignore.deps = c('rlang', 'fs' ) )

```


### Descriptives
```{r Descriptives of experiment results}

## graph of the distribution of the participants' rankings or results? 

```


### Participant Demographics
```{r Demographics of participants}

## number of participants

## gender

## age

## graph

```


### H1 (Main Effect) Analysis (replace this with description of H1)

#### How does [main effect variable] influence [results]?

```{r H1}

## analysis and p-value of H1

## graph of H1

```

### Exploratory Analysis (replace this with description)

#### How does [exploratory variable] influence [results]?

```{r Exploratory}

## analysis and p-value

## graph
```



### Power Analysis 

```{r Power analysis}


set.seed(2532)

PowerModel = "" ##replace with main effect analysis

## use this line to extend the number of trials
PowerModelExt = extend(PowerModel, within = "participant_id+ratingType", n = 50)

## use this line to extend the number of participants
PowerModelExt = extend(PowerModelExt, along = "participant_id", n = 200)

## run sim
powerSim(PowerModelExt, nsim=1000)

# model the curve of this hypothetical experiment
pc <-  powerCurve(PowerModelExt, nsim = 1000, along = "participant_id") 

# plot and numbers
pc 
plot(pc)

```